Accurate Measurement of Bicycle Parameters

### 2010-10-19 papers/BMD2010/PhysicalParametersPoster/poster.tex
bode plot titles, spaces in a m file, poster final draft

  % Info about the model
  \begin{alertblock}{Whipple Bicycle Model}
    \rmfamily{
    The linear unforced two degree-of-freedom, $\mathbf{q}$
    = [steer and roll], linear Whipple model takes the form:
    \small{
    \begin{equation}
        \mathbf{M\ddot{q}}
        +v\mathbf{C}_1\mathbf{\dot{q}}
        +\left[g\mathbf{K}_0
        +v^2\mathbf{K}_2\right]\mathbf{q}
        =0
        \label{eq:canonical}
    \end{equation}
    }
    Where the entries to the $\mathbf{M}$, $\mathbf{C}_1$, $\mathbf{K}_0$ and $\mathbf{K}_2$
    matrices are combinations of 25 of the bicycle's physical parameters that
    include the geometry, mass, mass location and mass distribution of the four
    rigid bodies.
    }
  \end{alertblock}

@@

  \begin{block}{Accuracy}
    \rmfamily{
    Following the vain of \cite{Roland1971} we used error propagation theory to
    calculate accuracy of the 25 benchmark bicycle parameters. We estimate
    the standard deviation of the raw measurements. If $x$ is a parameter and is a function of
    the raw measurements, $u,v,\ldots$, then $x$ is a random variable defined as
    $x=f(u,v,\ldots)$. The sample variance of $x$ is defined as
    \begin{equation}
        s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
                s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
                2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
                + \ldots
        \label{eqn:variance}
    \end{equation}
    where $s_*$ is the variance and $s_{**}$ is the covariance. If $u$ and $v$ are uncorrelated then $s_{uv}=0$ but the cross correlations
    must be taken into account otherwise.
    }
  \end{block}
  \begin{columns}[t, totalwidth=\twocolwid]
      \begin{column}{\onecolwid}
          \begin{block}{Bicycles}
            \rmfamily{
            The six bicycles, chosen for both variety and convenience, are as follows:
            \emph{Batavus Browser}, a Dutch style city bicycle measured with and without
            instrumentation; \emph{Batavus Stratos
            Deluxe}, a Dutch style sporty city bicycle; \emph{Batavus Crescendo Deluxe} a
            Dutch style city bicycle with a suspended fork; \emph{Gary Fisher Mountain
            Bike}, a hardtail mountain bicycle; \emph{Bianchi Pista}, a modern steel frame
            track racing bicycle; and \emph{Yellow Bicycle}, a stripped down aluminum frame
            road bicycle measured in two configurations, the second with the fork rotated
            in the headtube 180 degrees for larger trail.
            \\
            \begin{center}
                \begin{tabular}{ccc}
                    \includegraphics[width=0.333\onecolwid]{../../../images/browserIns_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/crescendo_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/fisher_sub.jpg}
                    \\
                    \includegraphics[width=0.333\onecolwid]{../../../images/pista_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/stratos_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/yellow_sub.jpg}
                \end{tabular}
            \end{center}
            }
          \end{block}
    \end{column}

@@

        \begin{block}{Measurements}
            \rmfamily{
            We attempted to directly measure the trail, wheelbase and wheel
            diameters with various techniques. We measured the mass centers of
            the four bodies (fork, frame, and wheels) by hanging the bodies by
            their mass centers. The moments of inertia were estimated by
            hanging the bodies as both torsional and compound pendulums and
            measuring the period of oscillation which is correlated to the
            inertia.
            }
            \begin{center}
              \includegraphics[width=0.90\onecolwid]{../../../figures/angles.pdf}
            \end{center}
        \end{block}

    \end{column}
\end{columns}

@@

% The fourth column
\begin{column}{\onecolwid}
  \begin{alertblock}{Bike Eigenanalysis}
    \rmfamily{
    Distinct variation is apparent among the bicycles' eigenvalues. Frequency,
    damping, and the stable speed range can be compared to the physical
    differences of the bicycles.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/Bike/eig_plot.pdf}
    \end{center}
    \rmfamily{
    Less variation is seen among the bicycles when the mass and inertia of a
    rigid rider is added.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/BikeRider/eig_plot.pdf}
    \end{center}
  \end{alertblock}

\begin{column}{\onecolwid}
  % Frequency Response
  \begin{block}{Bike Frequency Response}
    \rmfamily{
    The steer torque to roll angle Bode plot reveals up to 10 dB variation
    among the bikes along the frequencies shown.
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/Bike/Bode/Tdel2phi.pdf}
    \end{center}
    }
  \end{block}

  % Frequency Response
  \begin{block}{Bike/Rider Frequency Response}
    \centering
    \includegraphics[width=.9\onecolwid]{../../../plots/BikeRider/Bode/Tdel2phi.pdf}
  \end{block}

>>>>

  % Info about the model
  \begin{alertblock}{Whipple Bicycle Model}
    \small{\rmfamily{
    The linear unforced two degree-of-freedom, $\mathbf{q}$
    = [steer and roll], linear Whipple model takes the form:
    \begin{equation}
        \mathbf{M\ddot{q}}
        +v\mathbf{C}_1\mathbf{\dot{q}}
        +\left[g\mathbf{K}_0
        +v^2\mathbf{K}_2\right]\mathbf{q}
        =0
        \label{eq:canonical}
    \end{equation}
    Where the entries to the $\mathbf{M}$, $\mathbf{C}_1$, $\mathbf{K}_0$ and $\mathbf{K}_2$
    matrices are combinations of 25 of the bicycle's physical parameters that
    include the geometry, mass, mass location and mass distribution of the four
    rigid bodies.
    }}
  \end{alertblock}

@@

  \begin{block}{Accuracy}
    \rmfamily{
    Following the vain of \cite{Roland1971} we used error propagation theory to
    calculate accuracy of the 25 benchmark bicycle parameters. We estimate
    the standard deviation of the raw measurements. If $x$ is a parameter and is a function of
    the raw measurements, $u,v,\ldots$, then $x$ is a random variable defined as
    $x=f(u,v,\ldots)$. The sample variance of $x$ is defined as
    \begin{equation}
        s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
                s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
                2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
                + \ldots
        \label{eqn:variance}
    \end{equation}
    where $s_u$ is the variance and $s_{uv}$ is the covariance. If $u$ and $v$ are uncorrelated then $s_{uv}=0$ but the cross correlations
    must be taken into account otherwise.
    }
  \end{block}
  \begin{columns}[t, totalwidth=\twocolwid]
      \begin{column}{\onecolwid}
          \begin{block}{Bicycles}
            \rmfamily{
            The six bicycles, chosen for both variety and convenience, are as follows:
            \emph{Batavus Browser}, a Dutch style city bicycle measured with and without
            instrumentation; \emph{Batavus Stratos
            Deluxe}, a Dutch style sporty city bicycle; \emph{Batavus Crescendo Deluxe} a
            Dutch style city bicycle with a suspended fork; \emph{Gary Fisher Mountain
            Bike}, a hardtail mountain bicycle; \emph{Bianchi Pista}, a modern steel frame
            track racing bicycle; and \emph{Yellow Bicycle}, a stripped down aluminum frame
            road bicycle measured in two configurations, the second with the fork rotated
            in the headtube 180 degrees for larger trail.
            \\
            \begin{center}
                \begin{tabular}{ccc}
                    \includegraphics[width=0.333\onecolwid]{../../../images/browserIns_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/crescendo_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/fisher_sub.jpg}
                    \\
                    \includegraphics[width=0.333\onecolwid]{../../../images/pista_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/stratos_sub.jpg} &
                    \includegraphics[width=0.333\onecolwid]{../../../images/yellow_sub.jpg}
                \end{tabular}
            \end{center}
            }
          \end{block}
    \end{column}

@@

  \begin{alertblock}{Bicycle Eigenanalysis}
    \rmfamily{
    Distinct variation is apparent among the bicycles' eigenvalues. Frequency,
    damping, and the stable speed range can be compared to the physical
    differences of the bicycles. The bicycles also exhibit a two imaginary root
    pairs at low speeds.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/Bike/eig_plot.pdf}
    \end{center}
    \rmfamily{
    Less variation is seen among the bicycles when a
    rigid rider is added, except in the stable sppeed ranges.
    }
    \\
    \begin{center}
      \includegraphics[width=.9\onecolwid]{../../../plots/BikeRider/eig_plot.pdf}
    \end{center}
  \end{alertblock}

    \end{column}
\end{columns}
\end{column}

% The fourth column
\begin{column}{\onecolwid}
        \begin{block}{Measurements}
            \rmfamily{
            We estimated the wheel radii by measuring the distance traveled
            by the loaded wheels, the trail by directly measuring the fork
            offset and the wheelbase and headtube angle by direct measurement.
            We measured the mass of the four bodies (fork, frame, and
            wheels) directly using an precision scale. We found the location of
            the mass center by hanging the bodies in multiple orientations
            through their mass centers.
            }
            \\
            \begin{center}
              \includegraphics[width=0.8\onecolwid]{../../../figures/angles.pdf}
            \end{center}
            \rmfamily{
            The in- and out-of-symmetric plane moments of inertia were estimated by
            hanging the bodies as torsional and compound pendulums,
            respectively. We then estimated the period of oscillation by
            fitting a decaying osciallation function to a voltage signal from a
            rate gyro after the pendulums were perturbed. The period can then
            be correlated to the inertia.
            }
            \\
            \begin{center}
              \includegraphics[width=0.90\onecolwid]{../../../plots/PendFit/BrowserFrameCompoundFirst1.pdf}
            \end{center}
        \end{block}

@@

\begin{column}{\onecolwid}
  % Frequency Response
  \begin{alertblock}{Bicycle Frequency Response}
    \small{\rmfamily{
    The steer torque to roll angle Bode plot reveals up to 10 dB variation
    among the bikes and variation in phase.
    }}
    \\
    \begin{center}
      \includegraphics[width=.85\onecolwid]{../../../plots/Bike/Bode/Tdel2phi.pdf}
      \\
      \includegraphics[width=.85\onecolwid]{../../../plots/BikeRider/Bode/Tdel2phi.pdf}
    \end{center}
  \end{alertblock}
